\documentclass[english,a4paper,12pt,twoside]{article}

\usepackage[T1]{fontenc}

% UTF-8 support
\usepackage{ucs} % provides utf8x input encoding
\usepackage[utf8x]{inputenc}

% language and regional settings
\usepackage[icelandic,english]{babel}

% smaller margins
\usepackage[margin=2cm, bottom=2.8cm]{geometry}

\usepackage{pdflscape}

\usepackage{fancyhdr}
\pagestyle{fancyplain}
\fancyhf{}
\renewcommand{\headrulewidth}{0cm}
\headheight 31pt

\lhead{\small Software Development\\HBV401G}
\chead{\large Assignment 1a\\\normalsize Team 8H}
\rhead{\small hths17@hi.is, rak4@hi.is\\ vab18@hi.is}

\title{
  \Large HBV401G Software Development\\
  \Huge Assignment 1a\\
  Team 8H
}
\author{
  Hannes Þór Sveinbjörnsson (hths17@hi.is)\\
  Ragnheiður Ásta Karlsdóttir (rak4@hi.is)\\
  Viktor Alex Brynjarsson (vab18@hi.is)\\
}

\begin{document}

\maketitle
\thispagestyle{empty}
\clearpage
\setcounter{page}{1}
\newpage
\pagenumbering{arabic}
\cfoot{\thepage}

\subsubsection*{Search}
\begin{itemize}
  \item As a user, I want to find a hotel by name so that I can find available rooms in that hotel.
  \item As a user, I want to find hotel rooms by location so that my search results all fit my geographical needs.
  \item As a user, I want to find hotel rooms by availability (dates and length of stay) so that I know the search results are available at the time I will need a room.
  \item As a user, I want to filter my search results by price so that I can find a hotel room in my price range.
  \item As a user, I want to filter my search results by hotel rating so that I can find a hotel room which is up to standard.
  \item As a user, I want to filter my search results by the number of beds so that I can find a room with adequate accommodation.
  \item As a user, I want to filter my search results by the type of bed so that I can find a room with the bed of my preference.
  \item As a user, I want to filter my search results by amenities (WIFI, breakfast included, 24/7 reception, room service, etc.) so that so that the search results will reflect my needs.
\end{itemize}

\subsubsection*{Viewing hotels}
\begin{itemize}
  \item As a user, I want to see details of the types of rooms in a specific hotel so that I know that the rooms available fit my needs.
  \item As a user, I want to be able to see the availability of rooms in a specific hotel so that I know that I can book the rooms I require.
  \item As a user, I want to see the location of the hotel on a map so that I can verify that it is in the location I am satisfied with.
  \item As a user, I want to see images of the hotel rooms and the hotel so that I can be assured of it's quality and that it fits my needs.
  \item As a user, I want to see reviews and ratings of the hotel by other guests so that I can be asassured of it's quality and that it fits my needs.
  \item As a user, I want to see the interest in a hotel (5 people have viewed this hotel in the last hour, only 4 rooms available at this time) so that I am more likely to book.
\end{itemize}

\subsubsection*{Booking a room}
\begin{itemize}
  \item As a user, I want to book rooms (one or more) in a specific hotel for a certain number of nights at a certain date so that I know I have rooms available to me when I come to stay.
  \item As a user, I want to be able to pay for my stay in advance so that I don't have to worry when I get there.
\end{itemize}

\end{document}
